### 2023-02-08 article.tex
Progress

\paragraph{Code is vital}

The code for this experiment is vital paradata.
Ideally, the code is useful paradata, 
as discussed in section \label{sec:making-code-useful-paradata}.

@@

Again, paradata should be comprehensive, comprehensively documented
and friendly to computers \cite{huvila2022improving}.
In this section, these ideal properties of paradata are applied to code.
The resulting recommendations are compared with
existing best practices in writing code.

@@

There is another problem that authors of academic code face,
which is that they may be contacted with a user 
asking for technical report 
(against which a 'no' is just fine \cite{barnes2010publish})
or -more relevant to the research- sending in a bug report.
One solution for the author is to ignore such emails
and it can be argued that no energy should be wasted on published code
and work on something new instead 
(see \cite{barnes2010publish} for a better way to deal with the problem).

>>>>

@@

Again, paradata should be comprehensive, documented in a useful way
and friendly to computers \cite{huvila2022improving}.
In this section, these ideal properties of paradata are applied to code.
The resulting recommendations are compared with
existing best practices in writing code.

@@

There is another problem that authors of academic code face,
which is that they may be contacted with a user 
asking for technical report 
(against which a 'no' is just fine \cite{barnes2010publish})
or -more relevant to the research- sending in a bug report.
One solution for the author is to ignore such emails (as is done in a third
of all cases \cite{teunis2015corresponding}):
it can be argued that no energy should be wasted on published code
and work on something new instead 
(see \cite{barnes2010publish} for a better way to deal with the problem).
